\documentclass[12pt]{exam}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.8in}
\setlength{\parindent}{0in}
\setlength{\parskip}{\baselineskip}

\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{ dsfont }
\usepackage{tikz}
\title{CSCI-246 Discrete Structures \\ HW 12 -- Final Homework}
\author{Instructor: Adiesha Liyanage}
\date{November 15 2024}

\begin{document}

\maketitle

\hrulefill
\\
\\
\textbf{Objective}
\begin{itemize}
    \item Understanding counting.
    \item Understanding asymptotic analysis.
    \item Understanding properties of Big O.
    \item Understanding algorithm analysis.
    \item Understanding problem solving process. 
\end{itemize}

\textbf{Submission requirements}
\begin{itemize}
    \item \textbf{\textit{Type or clearly hand-write}} your solutions into a \textbf{\textit{PDF FORMAT.}} 
    \item \textbf{\textit{DO NOT UPLOAD images.}}
    \item \textbf{\textit{non-pdf or emailed solutions will not be graded.}}
    \item \textbf{If you take pictures of your handwritten homework, put it into pdf format.}
    \item \textbf{\textit{Start each problem on a new page.}}
    \item Follow the model that you have learned during the lectures for proofs.
    \item Do not wait until the last minute to submit the assignment.
    \item You can submit any number of times before the deadline. 
    \item If you are using latex, and you do not know how to type a symbol, use the following website. You can draw the symbol here and it will give you the latex code and the packages that you have to import. \url{https://detexify.kirelabs.org/classify.html}
    \item If you are using latex to write the answer, you can use overleaf to make your life easier. \textbf{Overleaf is a free, online platform that helps users create and publish scientific and technical documents using LaTeX, a markup-based document preparation system}
    \item If you do not understand a problem, ask questions during/after the lectures, or during office hours or via discord.
    \item Go to TA office hours and talk with them and ask for help.
    \item \textbf{\textit{Do not use generative AI to write answers.}} 
\end{itemize}


\section{Q1}
If we roll a fair 3-sided die 11 times, what is the number of ways that we can get 4 1’s, 5 2’s, and 2 3’s? Show your work.

\section{Q2}


\begin{enumerate}
    \item Prove that $3n^4 + 4n^2 - 2n = O(n^4)$ by constructing $c > 0$, $n_0 \geq 0 : \forall n \geq n_0 : 3n^4 + 4n^2 - 2n \leq c \cdot n^4.$
\end{enumerate}

\section{Q3}
In class we proved that $n^3 \neq O(n^2)$. Following that proof, fill the blanks, to show that $3n^4 + 4n^2 -2n \neq O(n^3)$ by disproving $\exists c > 0, n_0 \geq 0 : \forall n \geq n_0 : 3n^4 + 4n^2 -2n \leq c \cdot n^3$.

To disprove $\exists c > 0, n_0 \geq 0 : \forall n \geq n_0 : 3n^4 + 4n^2 -2n \leq c \cdot n^3$, we need to show that: $\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_$.

So we show how to construct $\_\_\_\_\_\_$, given any $\_\_\_\_\_\_$, and $\_\_\_\_\_\_\_\_\_\_$.

Let $c > 0$ and $n_0 \geq 0$. Let $n = max(n_0, c + 1)$, then consider $n = c + 1$.

\[3n^4 + 4n^2 -2n = \text{fill in here and take as much as lines you need}\]


which is $\_\_\_\_\_\_ > c \cdot (c + 1)^3$. Therefore, we have shown how to produce a $n \geq n_0$ such that $3n^4 + 4n^2 -2n > c \cdot n^3$, for any $c, n_0$ value, meaning that $3n^4 + 4n^2 -2n$ is not $O(n^3)$.



\section{Q4}
\begin{enumerate}
    \item Give two functions, $f$ and $h$, such that $f = O(n^3)$ and $h = O(2^n)$ but $f(n)  \neq O(h(n))$.

    Note that you only need to pick $f,h$ that follows the given restriction.
    \item Now that you have picked $f,h$, prove that $f = O(n^3)$ and $h = O(2^n)$.

    \item Use that same $f,h$ functions and prove that $f(n) \neq O(h(n))$.
\end{enumerate}
\end{document}
